Montreal Real Estate Pricing \\ {\normalsize Code available at: \url{https://github.com/mike-n-7/ML4}}

### 2014-12-04 Paper/paper.tex
finished algorithm descriptions.

\usepackage{amsmath}
\usepackage{verbatim}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{url}
\usepackage{multicol}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usepackage{wasysym}

@@

\subsection{Algorithm Selection}
	Below is a brief description of the algorithms considered.

\subsubsection{Linear Regression}
\subsubsection{Lasso Regression}
\subsubsection{K Nearest Neighbours}

>>>>

\usepackage{amsmath}
\usepackage{verbatim}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{url}
\usepackage{multicol}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usepackage{wasysym}
\usepackage{mathtools}
\DeclarePairedDelimiter{\abs}{\lvert}{\rvert}

@@

\subsection{Algorithm Selection}
	Below is a brief description of the algorithms considered. They were chosen from a wider set of algorithms because during initial smoke testing they had the best results and showed promise.

\subsubsection{Linear Regression}
	Linear Regression is a simple and classic method that fits a line/plane through the data in the space of features. It's hypothesis for a feature space with m features is of the form, \\
	\[  f_{w}(x) = w_{0}  + \sum_{j=1:m}w_{j}x_{j} \] \\

	The w's are the weights that need to be solved for. Different approaches exist for picking these weights optimally. The scikit-learn implementation uses least-squares which seeks to choose a weight vector to minimize,
	\[ Err(w)  = \sum_{i=1:n}(y_{i} - w^{T}x_{i})^{2}\] \\

	A closed form solution does exist but the remaining details, while interesting, are not pertinent.

\subsubsection{Lasso Regression}
	Lasso Regression is similar in nature to Linear Regression but makes a number of improvements. It is a form of \emph{regularization} which aims to impose constraints on a solution to prevent overfitting. In Lasso Regression, the weights are constrained by penalizing by their absolute value. This forces less important features to have weights of 0 and implicitly weeds out useless features in the process. Because the real estate domain is a bit foreign to us, we simply included features we felt might have influence on property price. This algorithm will help trim them down to a relevant subset.

	It solves for a weight vector s.t. \\
	\[ w^{lasso} = argmin_{w}(\sum_{i=1:n}(y_{i} - w_{0} - \sum_{j=1:m}x_{ij}w_{j})^{2} + \lambda\sum_{j=1:m}\abs{w_{j}}) \]

\subsubsection{K Nearest Neighbours}
	K nearest neighbours take a different approach. The core assumption made with this method is that examples with similar feature values should have similar outputs. Neighbours of a queried datapoint should be used to determine it's value and not points that are far away. In a regression task, once the neighbours have been located, the mean of their values (or a weighted average) is taken to assign to the queried point.

	The scikit-learn implementation takes a basic average of the neighbouring data to predict new values. This method is very intuitive but performance really can depend on the nature of the dataset involved. In our case it seems like a very good option because homes tend to be priced similarly to homes in the same (literal) neighbourhood. Beyond the fact that the algorithms name seems apt, it should be able to capture this assumption regarding real estate as literal neighbours will have similar construction dates, sizes and proximity to infrastructure.
